Automatic word stress annotation of Russian running text (max 8 pages)

### 2015-01-20 rusaccent-nodalida-2015/rusaccent.tex
boldfaced important numbers in results table
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58476 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{table*}[t]
  \centering
  \begin{tabular}{r | r r r | r r }
    approach & accuracy\% & error\% & abstention\% & totTry\% & totFail\% \\
    \hline
    \hline
    {\small {\tt noCGbare}} & 30.43 & 0.17 & 69.39 & 30.61 & 69.57 \\
    {\small {\tt noCGsafe}} & 90.07 & 0.49 & 9.44 & 90.56 & 9.93 \\
    {\small {\tt noCGguess}} & 94.34 & 3.36 & 2.30 & 97.70 & 5.66 \\
    {\small {\tt noCGguessFreq}} & 95.53 & 2.59 & 1.88 & 98.12 & 4.47 \\
    {\small {\tt noCGguessSyll}} & 94.99 & 4.05 & 0.96 & 99.04 & 5.01 \\
    {\small {\tt noCGguessFreqSyll}} & 95.83 & 3.46 & 0.72 & 99.28 & 4.17 \\
    \hline
    {\small {\tt CGbare}} & 45.78 & 0.44 & 53.78 & 46.22 & 54.22 \\
    {\small {\tt CGsafe}} & 93.21 & 0.74 & 6.05 & 93.95 & 6.79 \\
    {\small {\tt CGguess}} & 95.50 & 2.59 & 1.90 & 98.10 & 4.50 \\
    {\small {\tt CGguessFreq}} & 95.73 & 2.40 & 1.88 & 98.12 & 4.27 \\
    {\small {\tt CGguessSyll}} & 95.92 & 3.33 & 0.74 & 99.26 & 4.08 \\
    {\small {\tt CGguessFreqSyll}} & 96.15 & 3.14 & 0.72 & 99.28 & 3.85 \\
    \hline
    {\small {\tt RussianGram}} & 90.09 & 0.79 & 9.12 & 90.88 & 9.91
  \end{tabular}
  \caption{Results of stress placement task evaluation. (N = 4048)}
  \label{tab:results}
\end{table*}

>>>>

\begin{table*}[t]
  \centering
  \begin{tabular}{r | r r r | r r }
    approach & accuracy\% & error\% & abstention\% & totTry\% & totFail\% \\
    \hline
    \hline
    {\small {\tt noCGbare}} & 30.43 & 0.17 & 69.39 & 30.61 & 69.57 \\
    {\small {\tt noCGsafe}} & \bf{90.07} & 0.49 & 9.44 & 90.56 & 9.93 \\
    {\small {\tt noCGguess}} & 94.34 & 3.36 & 2.30 & 97.70 & 5.66 \\
    {\small {\tt noCGguessFreq}} & 95.53 & 2.59 & 1.88 & 98.12 & 4.47 \\
    {\small {\tt noCGguessSyll}} & 94.99 & 4.05 & 0.96 & 99.04 & 5.01 \\
    {\small {\tt noCGguessFreqSyll}} & 95.83 & 3.46 & 0.72 & 99.28 & 4.17 \\
    \hline
    {\small {\tt CGbare}} & 45.78 & 0.44 & 53.78 & 46.22 & 54.22 \\
    {\small {\tt CGsafe}} & \bf{93.21} & 0.74 & 6.05 & 93.95 & 6.79 \\
    {\small {\tt CGguess}} & 95.50 & 2.59 & 1.90 & 98.10 & 4.50 \\
    {\small {\tt CGguessFreq}} & \bf{95.73} & \bf{2.40} & 1.88 & 98.12 & 4.27 \\
    {\small {\tt CGguessSyll}} & 95.92 & 3.33 & 0.74 & 99.26 & 4.08 \\
    {\small {\tt CGguessFreqSyll}} & \bf{96.15} & \bf{3.14} & 0.72 & 99.28 & 3.85 \\
    \hline
    {\small {\tt RussianGram}} & \bf{90.09} & 0.79 & 9.12 & 90.88 & 9.91
  \end{tabular}
  \caption{Results of stress placement task evaluation. (N = 4048)}
  \label{tab:results}
\end{table*}
